SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
some other edits

%make them more pointy, shorten it. mainly the first paragraph

Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}. They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{CommitmentScheme}) to prevent front-running. Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{submarineCommits}.

Double-spending attacks in Bitcoin have also been studied~\cite{bamert2013have,karame2012double} where a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed. The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first. We think of this as a type of front-running.

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

\paragraph{Commit/Reveal.}

>>>>

%make them more pointy, shorten it. mainly the first paragraph
% Jeremy: agree with above, also should be organized into subjects not just a list of papers

Front-running is mentioned in passing in many papers and we try to 
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to market information leakage~\cite{aune2017footprints}. They also propose a cryptographic approach, similar to commit and reveal (see Section~\ref{sec:comm}) to prevent front-running. Malinova and Park discuss different design settings for financial markets and trading platforms on decentralized ledgers~\cite{malinova2017market}. They argue that blockchain brings new options of transparency which affects traders behaviour, especially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient. Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which extend commit and reveal; we discuss them further in Section~\ref{sec:comm}.

Double-spending attacks in Bitcoin are related to front-running~\cite{bamert2013have,karame2012double}. In this attack, a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed. The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first. This can be considered a form of self-front-running.

In the cryptographic literature, front-running attacks are modelled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

\paragraph{Commit/Reveal.}
\label{sec:comm}
